The \project{unRAVE} catalog of stellar atmospheric parameters and\\ chemical abundances for chemo-dynamic studies in the \gaia\ era

### 2016-09-09 article/unrave.tex
fix order

\author{Andrew R. Casey\altaffilmark{1}, Keith Hawkins\altaffilmark{1}, David W. Hogg\altaffilmark{2,3,4,5}, Melissa Ness\altaffilmark{5}, Hans Walter-Rix\altaffilmark{5}, Georges Kordopatis\altaffilmark{6}, Andrea Kunder\altaffilmark{6}, Matthias Steinmetz\altaffilmark{6}, Harry Enke\altaffilmark{6}, Jason Sanders\altaffilmark{1}, Sergey Koposov\altaffilmark{1}, Gerry Gilmore\altaffilmark{1}, Toma\v{z} Zwitter\altaffilmark{6}, Kenneth C. Freeman\altaffilmark{7}, Luca Casagrande\altaffilmark{7}, 
Gal Matijevic\altaffilmark{6}, George Seabroke\altaffilmark{8}, Olivier Bienayme\altaffilmark{9}, 
Joss Bland-Hawthorn\altaffilmark{10}, Brad K. Gibson\altaffilmark{11}, Eva~K.~Grebel\altaffilmark{12}, Amina Helmi\altaffilmark{13}, Ulisse Munari\altaffilmark{14}, Julio F. Navarro\altaffilmark{15,16}, Warren Reid\altaffilmark{17,18}, Arnaud Siebert\altaffilmark{19}, Rosemary Wyse\altaffilmark{20}\\
\vspace{2em}
\emph{(Affiliations can be found at the end of the article)}
}

>>>>

\author{
Andrew R. Casey\altaffilmark{1}, 
Keith Hawkins\altaffilmark{1}, 
David W. Hogg\altaffilmark{2,3,4,5}, 
Melissa Ness\altaffilmark{5}, 
Hans Walter-Rix\altaffilmark{5}, 
Georges Kordopatis\altaffilmark{6}, 
Andrea Kunder\altaffilmark{6}, 
Matthias Steinmetz\altaffilmark{6}, 
Sergey Koposov\altaffilmark{1}, 
Harry Enke\altaffilmark{6}, 
Jason Sanders\altaffilmark{1}, 
Gerry Gilmore\altaffilmark{1}, 
Toma\v{z} Zwitter\altaffilmark{6}, 
Kenneth C. Freeman\altaffilmark{7}, 
Luca Casagrande\altaffilmark{7}, 
Gal~Matijevic\altaffilmark{6}, 
George Seabroke\altaffilmark{8}, 
Olivier Bienayme\altaffilmark{9}, 
Joss Bland-Hawthorn\altaffilmark{10}, 
Brad~K.~Gibson\altaffilmark{11}, 
Eva~K.~Grebel\altaffilmark{12}, 
Amina Helmi\altaffilmark{13}, 
Ulisse Munari\altaffilmark{14}, 
Julio F. Navarro\altaffilmark{15,16}, 
Warren Reid\altaffilmark{17,18}, 
Arnaud Siebert\altaffilmark{19},
Rosemary Wyse\altaffilmark{20}\\
\vspace{2em}
\emph{(Affiliations can be found at the end of the article)}
}
